All just Greedy for Money? - A prediction and Analysis of the interplay between Graduate Statistics and Salary Prospects in the STEM Field

### 2024-01-28 doc/DataLiteracyStudentProject/paper.tex
revised abstract

% if you use cleveref..
\usepackage[capitalize,noabbrev]{cleveref}

@@

\twocolumn[
\icmltitle{All just Greedy for Money? - An Prediction and Analysis of the interplay between Graduate Statistics and Salary Prospects in the STEM Field}

@@

%Put your abstract here. Abstracts typically start with a sentence motivating why the subject is interesting. Then mention the data, methodology or methods you are working with, and describe results. 
\begin{abstract}
This paper examines whether the expected salary plays a role in which subject graduates choose to study. We have limited ourselves to the STEM (science, technology, engineering and maths) field. We analyse the influence of the three parameters: number of Graduates, of Students and Expected Salary, have on each other. Therefore we use the Vector autoregressive model and a PACF. This showed that the expected salary has an \textcolor{red}{or has no?} influence on how many school leavers decide to study in the STEM field. We were also able to make the prediction that the expected salary and the number of students in the next two years will be similar to the current situation, but slightly reduced. If the salary is increased or decreased in the analysis, it can be seen that the number of students goes up or down accordingly.(\textcolor{red}{or else?})
%Motivate the problem, situation or topic you decided to work on. 
% Describe why it matters (is it of societal, economic, scientific value?). 
% Outline the rest of the paper (use references, e.g.~to \Cref{sec:methods}: 
% What kind of data you are working with, how you analyse it, and what kind of conclusion you reached. 
% The point of the introduction is to make the reader want to read the rest of the paper.
\end{abstract}

>>>>

% if you use cleveref.
\usepackage[capitalize,noabbrev]{cleveref}

@@

\twocolumn[
\icmltitle{All just Greedy for Money? - A prediction and Analysis of the interplay between Graduate Statistics and Salary Prospects in the STEM Field}

@@

%Put your abstract here. Abstracts typically start with a sentence motivating why the subject is interesting. Then mention the data, methodology, or methods you are working with, and describe results. 
\begin{abstract}
This paper investigates the role of expected salary in influencing the choice of academic majors among
students in the STEM field at the University of Tübingen.
The study focuses on the interplay among three key parameters: the enrollment of students, the expected salary, and the number of graduates.
Employing a Vector Autoregressive model, we can confidently predict the number of students for the upcoming semesters
and show that the expected salary plays a key role in making that prediction.
Furthermore, by manipulating the salary variable in our analysis, we observe a corresponding increase or decrease in the number of students.
This implies a sensitivity in enrollment trends to changes in expected salary, highlighting the potential impact of financial considerations on academic choices.

% Motivate the problem, situation, or topic you decided to work on. 
% Describe why it matters (is it of societal, economic, or scientific value?). 
% Outline the rest of the paper (use references, e.g.~to \Cref{sec:methods}: 
% What kind of data you are working with, how you analyze it, and what kind of conclusion you reached. 
% The point of the introduction is to make the reader want to read the rest of the paper.
\end{abstract}
